\cvsection{Undergraduate Projects}
\vspace{-.5\baselineskip}
\begin{cventries}
  \cventry
    {Java, Javascript, Maven, Github, Restful API, React}
    {React Travel Site}
    {}
    {CS 314 Software Engineering}
    {
      \begin{cvitems}
        \item {Engaged with 3 other teammates in an Agile Development work environment.}
        \item {Performed code analysis on front end and back end.}
        \item {Maintainability through Travis CI, Code Climate, and Github.}
        \item {Optimized nearest neighbor using 2 opt and 3 opt algorithms.}
      \end{cvitems}
    }
      \cventry
    {Java, Python,MySQL, Java Swing}
    {Library Database and Interface}
    {}
    {CS 430 Database Systems}
    {
      \begin{cvitems}
        \item {Developed a MySQL Database and Interface Programs. Learned Java Swing to create a custom Database GUI}
        \item {Implemented custom file read in,error checking, and input into a database.}
        \item {Produced Console GUI and Java Swing GUI for database operations and searching.}
      \end{cvitems}
    }
  \cventry
    {Javascript, Python, C++, MQTT}
    {Demeter}
    {}
    {CS 370 Operating Systems}
    {
      \begin{cvitems}
        \item {Automated Gardening System using MQTT and Microcontrollers. https://github.com/zombodotcom/Demeter/}
        \item {Measures Temperature, Humidity, Light, Soil Moisture, and allows for Automated Watering.}
      \end{cvitems}
    }
  \cventry
    {SQL,HTML,FuelPHP}
    {State Attractions Website}
    {}
    {CT 310 Web Development }
    {
      \begin{cvitems}
        \item {Combined MySQL and a PHP MVC to create a Front and Back end of an attractions website.}
      \end{cvitems}
    }
\end{cventries}
\vspace{-1.5\baselineskip}
